\cvsection{Experience}
\begin{cventries}
  \cventry
  {Software Development Engineer}
  {Simply Vyapar Apps Pvt Ltd}
  {Bangalore, KA}
  {June 2021 - Present}
  {
    \begin{cvitems}
      \item {Worked with datastores like SQL, mongoDB, Redis, etc and MVC frameworks including NestJS, Handlebars, Laravel, Blade, etc.}
      \item {Implemented payment interface, monitoring and reverification system with Razorpay leading to reduction in drop-offs by 20\%.}
      \item {Created agent assignment, call scheduling, feedbacks and commissions management system for various internal support teams.}
    \end{cvitems}
  }
  \cventry
  {Software Development Engineer}
  {Hyperverge Inc.}
  {Bangalore, KA}
  {June 2020 - June 2021}
  {
    \begin{cvitems}
      \item {Worked on enhancement of microservice architecture and created a cloud-agnostic stack for SEA nations. Setup CI/CD using Gitlab.}
      \item {Converted the synchronous architecture to Asynchronous event-based architecture thereby reducing response times by about 40\%.}    
      \item {Set up performance monitoring system with elasticsearch as well as alerts using graphana and opsgenie to achieve 99.9\% uptime.}
      \item {Used tools like sentry, opentelemetry as well as set up test environment to reduce 5xx error rates to almost zero.}
      \item {Used kubernetes to setup a job orchestration and scheduling system for improving efficiency in GPU usage for model training.}
    \end{cvitems}
  }
  \cventry
    {Technology Intern}
    {Morningstar, Inc.}
    {Mumbai, MH}
    {Jul 2019 - Dec 2019}
    {
      \begin{cvitems}
        \item {Developed micro-services and RESTful APIs using AWS components such as s3, lambda, dynamoDB, CloudWatch, Splunk, etc.}
        \item {Performed extensive integration testing as well as unit testing for the same JUnit 5 and mockito framework.}
        \item {\textbf{Recognition:} Awarded Morningstar monthly SPOT Award for September 2019.}
      \end{cvitems}
    }
  \cventry
    {Research Intern}
    {Central Electrical Engineering Research Institute (CEERI – CSIR)}
    {Chennai, TN}
    {May 2017 - Jul 2017}
    {
      \begin{cvitems}
        \item {Worked on "Embedded Wireless-Enabled Plastic Waste Sorting System" using python language and Raspberry Pi Operating System.}
        \item {Implemented Spectral Angle Mapping Algorithm to segregate different kinds of plastics by comparing their NIRS spectra.}
        \item {Developed a GUI in python using tkinter toolkit for remote monitoring, spectral data collection and information management.}
      \end{cvitems}
    }

\end{cventries}
